Tunable Spectral Ordering of Magnetic Plasmon Resonances

### 2018-04-05 paper_winter_2017/paper.tex
updated figures, added citations, formatted coupling

Plasmon oligomers, or plasmon metamolecules, are clusters of noble metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields even though their individual nanoparticle building blocks do not. Since their discovery in 2004, such magnetic plasmon resonances have impacted a variety of applied and fundamental research from negative index metamaterials to quantum tunneling and Fano interferences \cite{Alu2006,Alu2008,Liu2011,Dionne2011,Qian2015,Dionne2016} [CITE US, NORDLANDER, SHALAEV]. Magnetic plasmons have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances \cite{Zhang2006,Zhang2007,NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}. The magnetic properties of single oligomers, i.e. those clusters composed of only one ring of MNPs, are now well understood based upon quasistatic models \cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}. So too are extendend two-dimensional networks of oligomers using quasistatic tight-binding models \cite{Schatz2003,Weick2013}. However, recently, a disconnect between these extremes and methods has been highlighted, revealing a lack of understanding of how oligomer assemblies behave in the so-called intermediate size regime \cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.

@@

In the following, we build a simple analytically-solvable model to demonstrate the size-dependent evolution of the magnetic plasmons in intermediate-size $N$-mers by including the effects of retardation in the mutual interaction of their underlying electric dipole plasmon resonances. Interestingly, as a function of size, the magnetic plasmons switch their ordering in analogy to the way that electric plasmons in hybridized nanoparticles switch order \cite{vonPlessen2007}. We further analyze the distinct radiative properties of these magnetic plasmons by computing the angle-resolved cathodoluminescence (CL) spectrum \cite{Hohenester2014,Coenen2011,CoPol2011,Polman2014}. Building from the intuition gained, we finally analyze the size-dependent evolution of the intermediate-size plasmonic nanoclusters measured in Ref. \cite{Engheta2017}. We find that the spectral ordering depends not only on aggregate size but also upon morphology, offering the ability to tune the magnetic plasmon spectrum. Such understanding may someday lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications benefit directly from the tunability of system's electric and magnetic response \cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09}.

\section{Model Theory}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{2mer_3mer_fields.pdf}
\caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers. Each system supports a number of closed-loop magnetic plasmon resonances equal to the number of rings in the system. The magnetic plasmons support an electric dipole moment (a, c, and d) support out-of-phase magnetic fields. The nodeless magnetic modes (b and e) support a net magnetic dipole moment are accessible to the magnetic field of light.}
\label{field_plots}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{field_plots} displays two model oligomer systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to the molecules naphthalene and phenalene. Mapping the electric plasmons of each nanoparticle onto harmonic oscillators is now well-understood \cite{ARPC} [CITE US], and forms the basis for modeling the collective magnetic plasmon responses. In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic behavior of the oligomer are
\begin{equation}
\ddot{\textbf{q}}_i +\omega_{\textrm{sp}}^2\textbf{q}_i = \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i),
\label{equation_of_motion}
\end{equation}
where $\omega_{\textrm{sp}}=\sqrt{\omega_{p}^2/(\varepsilon_\infty+2\varepsilon_b)-(\gamma/2)^2}$ is the complex Mie resonance frequency and $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$. Here, $\omega_p$ is the metal's bulk plasma frequency, $\varepsilon_{\infty}$ and $\varepsilon_b$ are the high-frequency and background dielectric functions, and $\gamma$ is well approximated by the Drude electron-ion scattering rate for the nanoparticle sizes under consideration. While the Drude frictional force is not explicitly included in the equations of motion, Drude friction does modify the frequency of the Mie resonance. The dipole moment $\textbf{d}_i = e\textbf{q}_i$ of each plasmon oscillator is restricted to lie in the plane of the oligomer at position $\textbf{r}_i$, and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j$th dipole evaluated at the position of the $i$th dipole. The electric field is defined by
\begin{equation}
\textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) - \frac{k^2}{r_{ij}}\left(\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right)\right\}\frac{e^{ikr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
\label{electric_field_lambda}
\end{equation}
where $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}=|{\bf r}_i-{\bf r}_j|$ and $k=\sqrt{\varepsilon_b}\omega/c.$ The field is decomposed into three parts---the near- ($r_{ij}^{-3}$), intermediate- ($r_{ij}^{-2}$), and far-field ($r_{ij}^{-1}$)---which together include all dipolar retardation effects \cite{Purcell1973}. Interestingly, the latter term carries the opposite sign of the former two. As will be shown in the following, it is because of both the relative magnitude and sign of these terms as well as the oscillatory behavior of $e^{ikr_{ij}}$ that the interactions can change character and switch from energy-lowering to energy-raising.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{2mer-3mer-eig.pdf}
\caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer. At small scales $r_0 < 5$ nm the magnetic modes are ordered as predicted using a quasistatic model, with NS (orange) lower in energy than aN (blue). This implies that for very small oligomer systems, the quasistatic approximation is still accurate. However, at sizes greater than $r_0 = 5$ nm and smaller than $r_0 = 20$ nm, the eigenmodes switch order. This is due to the dominance of the far-field term, which is evident from (b and d). Finally, at sizes greater than $r_0 = 20$ nm, the eigenmodes switch order again. Also plotted are simulated peak positions of each mode (dashed lines) to show agreement within 0.1 eV.}
\label{scaling}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{scaling} shows the predicted magnetic plasmon resonance energies from both Eq. (\ref{equation_of_motion}) and full-wave numerical electrodynamics simulation of the 2-mer and 3-mer with increasing $a$ \cite{Hohenester2012}. At small $a$, the magnetic modes preserve the quasistatic ordering predicted in previous work \cite{Cherqui2014}, which is to be expected when the oligomer system fits within an optical wavelength and the near-field dominates the electric field. As the system size increases, the resonance energies decrease and cross at $a \approx 7$ nm, and once more at $a \approx 20$ nm. The second crossing recovers the same spectral ordering as at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is correct again. Rather, both crossings are due entirely to retardation effects as can be seen from the total interaction energy 
\begin{equation}
U = -\frac{1}{2} \sum_{ij} \textbf{d}_i \cdot \textbf{E}_j(\textbf{r}_i),
\label{interactionenergy}
\end{equation}
between each pair of electric dipole plasmons within each magnetic plasmon mode. It is the inclusion of the far-field that causes the mode switching, as it carries the opposite sign of the near- and intermediate-field terms. Fig. \ref{scaling} shows the competition between these field components as well as their relative contributions to the total interaction energy. Inspection of Fig. \ref{scaling}c reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field. Perhaps more interestingly, in any dielectric medium with $\varepsilon_b > 1$ the crossing points are shifted towards smaller scale due to wavelength contraction. This can be explained through the impact of dielectric medium upon the interaction energy $U,$ which increases with increasing $\varepsilon_b$ due mostly to the far-field term's dependence upon $k^2$ \cite{Elsayed2008}. While previous work has explored the oscillatory nature of hybridized electric dipole plasmon resonances and radiation damping as a function of separation in noble metal dimers \cite{vonPlessen2007}, our work shows that magnetic plasmon resonances also oscillate with interparticle separation and can be understood by analysis of the different contributions to the dipole-dipole interaction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{differential_power_diagrams.pdf}
\caption{Magnetic field distributions of a magnetic dipole mode (a) and an electric dipole mode (c) in the xy-plane with corresponding radiation patterns (b and d) in the yz-plane. The magnetic dipole exhibits the expected dipolar doughnut, or two lobe, shape with a node along the z-axis. The electric dipole moment also shows the expected pattern with a node along the y-axis.}
\label{scattering}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{scattering} displays the differential scattering power profiles associated with the aN (a) and NS (b) magnetic plasmon resonances as well as their interference (c) for any $N$-mer with electric and magnetic dipoles oriented as descibed above. Since the aN mode has only a $z$-oriented magnetic dipole, its radiation pattern is orthogonal to that of the $y$-directed electric dipole of the NS mode. This means that asymmetry in the radiation pattern is due to the excitation of both modes. Thus, examination of the radiation directionality allows one to determine the net electric or magnetic dipole character. Such forward/backward scattering asymmetries have been predicted and demonstrated in metal-semiconductor core-shell nanoparticle assemblies, that similarly exploit the interference between electric and magnetic plasmons to direct light \cite{Kivshar2012}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{CL_incomplete.pdf}
\caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d). By choosing the beam positions marked on the diagrams and choosing different angles at which to measure the light emitted, the magnetic modes of each oligomer can be disentangled. The colored "x's" correspond to colored traces. The blue traces show a collection angle of $\phi = 3\pi/2$ and the orange traces are for $\phi = \pi$, while both have $\theta = \pi/4$. Simulating these CL experiments with $r_0 = 15$ nm shows the aN modes lower in energy than the NS modes, as predicted. WIth $r_0 = 30$ nm, the modes switch, again as predicted.}
\label{CL_2mer_3mer}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The previous section built up intuition on the directionality of light scattered by the magnetic modes of the 2-mer and 3-mer. This intuition informs the particular angles at which to collect CL spectra. Fig. \ref{CL_2mer_3mer} shows simulated point angle-resolved CL spectra of the 2-mer and 3-mer, with the electron beam position chosen so as to excite the aN (blue) and NS (orange) modes. Note however, due to the symmetry of the oligomers, the blue electron beam position excites not only the aN mode, but also weakly the NS mode. Since the radiation profile of the aN mode is orthogonal to that of the NS mode, it is possible to distinguish them by analyzing the angular distribution of emitted CL radiation. The angle-resolved CL spectra at two such angles are reported in Fig. \ref{CL_2mer_3mer}. These simulated spectra confirm the predictions of the model displayed in Fig. \ref{scaling}; specifically, between $a = 15 - 30$ nm, the aN and NS modes switch spectral order. The simulation also shows mode switching at $a\approx7$ nm, however, the splitting energies are too small to be experimentally detectable with conventional CL. Nevertheless, experimental confirmation of the secondary mode splitting is possible, and would verify both our analytical and numerical predictions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{kagan_fields.pdf}
\caption{Signed magnetic field magnitudes of the modes of the 13-particle (a, b, and c), 19-particle (d, e, and f), and 31-particle (g, h, and i) clusters. Similarly to the 2mer and 3mer from before, we present only those magnetic modes with either NS and electric dipole character (a, b, d, e, g, and h) or with aN and magnetic dipole character (c, f, and i).}
\label{kagan_fields}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{kagan_fields} displays the signed magnetic field magnitude of the aN (panel a) and NS (panel c) magnetic plasmon resonances of the 13-, 19-, and 31-particle nanoclusters. The black arrows denote the electric dipole moments of the individual MNPs within each magnetic plasmon mode, the magenta arrows denote the net electric dipole moment of the nanocluster, and the background color denotes the strength of the associated magnetic field. The net electric or magnetic dipole magnitude is denoted below each panel. Panels b and d display the energy-filtered electron energy-loss (EEL) profiles of these modes. It is important to note that each aN mode is weakly excitable from the middle MNP (as indicated by the low EEL probability surrounding it), while the NS mode is strongly excitable from the same location (as indicated by the high EEL probability surrounding it). In all cases, the NS mode is doubly degenerate as would be true of any structure with sixfold symmetry. In analogy to the oligomers, these magnetic modes are chosen because they are the simplest (i.e., lowest order) and their radiation patterns are spatially orthogonal.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{13_19_31_eigen.pdf}
\caption{Eigenenergies and interaction energies for the magnetic modes of the 13- (a and b), 19- (c and d), and 31-particle (e and f) clusters. Unlike the 2mer and 3mer, at very small values of $r_0$, the aN modes are lower in energy than the NS modes. However, for each system a crossing point does occur between $r_0 = 30$ nm and $r_0 = 40$ nm. While the modes of the 13-particle system behave as expected, the aN and NS modes of the larger clusters behave contrary to the intuition built from the earlier model systems. At larger sizes, instead of a monotonic decrease in eigenenergies, the modes exhibit an increase in energy. Looking at the interaction energies, it becomes clear that this is again due to retardation effects, as the term that contributes the most anti-bonding character to the total interaction energy is the far-field. Furthermore, the 31-particle system exhibits a second crossing, unlike the other two structures, and the increase in its eigenenergies is maximized at smaller sizes.}
\label{kagan_eigen}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{kagan_eigen} displays the evolution of the aN and NS magnetic resonances with size $a$ as dictated by the model. Here the size-dependent behavior of the nanocluster resonances is different due to the hexagonal packing as opposed to the open-ring structure of the $N$-mer. Nevertheless, the analytic model is capable of predicting the magnetic spectrum. Most surprising is the oscillatory behavior of the nanoclusters' magnetic resonances with size as opposed to the expected monotonic redshifting of those of the $N$-mer (see Fig. \ref{scaling}). Panels b and c display the total interaction energy $U$, and its near-, intermediate-, and far-field contributions, showing that this oscillatory behavior is due to retardation effects through the $e^{ikr_{ij}}$ factor in Eq. (\ref{electric_field_lambda}).

>>>>

Plasmon oligomers, or plasmon metamolecules, are clusters of noble metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields even though their individual nanoparticle building blocks do not. Since their discovery in 2004, such magnetic plasmon resonances have impacted a variety of applied and fundamental research from negative index metamaterials to quantum tunneling and Fano interferences \cite{Prodan2003,Shalaev2004,Alu2006,Alu2008,Liu2011,Dionne2011,Cherqui2014,Qian2015,Dionne2016,Cherqui2016}. Magnetic plasmons have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances \cite{Zhang2006,Zhang2007,NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}. The magnetic properties of single oligomers, i.e. those clusters composed of only one ring of MNPs, are now well understood based upon quasistatic models \cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}. So too are extendend two-dimensional networks of oligomers using quasistatic tight-binding models \cite{Schatz2003,Weick2013}. However, recently, a disconnect between these extremes and methods has been highlighted, revealing a lack of understanding of how oligomer assemblies behave in the so-called intermediate size regime \cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017,Fakhraai2018,Scherer2018}.

@@

In the following, we build a simple analytically-solvable model to demonstrate the size-dependent evolution of the magnetic plasmons in intermediate-size $N$-mers by including the effects of retardation in the mutual interaction of their underlying electric dipole plasmon resonances. Interestingly, as a function of size, the magnetic plasmons switch their ordering in analogy to the way that electric plasmons in hybridized nanoparticles switch order \cite{vonPlessen2007}. We further analyze the distinct radiative properties of these magnetic plasmons by computing the angle-resolved cathodoluminescence (CL) spectrum \cite{Hohenester2014,Coenen2011,CoPol2011,Polman2014}. Building from the intuition gained, we finally analyze the size-dependent evolution of the intermediate-size plasmonic nanoclusters measured in Ref. \cite{Engheta2017}. We find that the spectral ordering depends not only on aggregate size but also upon morphology, offering the ability to tune the magnetic plasmon spectrum. Such understanding may someday lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications benefit directly from the tunability of system's electric and magnetic response \cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09,Tian2018}.

\section{Model Theory}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{fig1.pdf}
\caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers. Each system supports a number of closed-loop magnetic plasmon resonances equal to the number of rings in the system. The magnetic plasmons support an electric dipole moment (a, c, and d) support out-of-phase magnetic fields. The nodeless magnetic modes (b and e) support a net magnetic dipole moment are accessible to the magnetic field of light.}
\label{field_plots}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{field_plots} displays two model oligomer systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to the molecules naphthalene and phenalene. Mapping the electric plasmons of each nanoparticle onto harmonic oscillators is now well-understood \cite{Cherqui2014,ARPC}, and forms the basis for modeling the collective magnetic plasmon responses. In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic behavior of the oligomer are
\begin{equation}
\ddot{\textbf{q}}_i +\omega_{\textrm{sp}}^2\textbf{q}_i = \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i),
\label{equation_of_motion}
\end{equation}
where $\omega_{\textrm{sp}}=\sqrt{\omega_{p}^2/(\varepsilon_\infty+2\varepsilon_b)-(\gamma/2)^2}$ is the complex Mie resonance frequency and $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$. Here, $\omega_p$ is the metal's bulk plasma frequency, $\varepsilon_{\infty}$ and $\varepsilon_b$ are the high-frequency and background dielectric functions, and $\gamma$ is well approximated by the Drude electron-ion scattering rate for the nanoparticle sizes under consideration. While the Drude frictional force is not explicitly included in the equations of motion, Drude friction does modify the frequency of the Mie resonance. The dipole moment $\textbf{d}_i = e\textbf{q}_i$ of each plasmon oscillator is restricted to lie in the plane of the oligomer at position $\textbf{r}_i$, and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j$th dipole evaluated at the position of the $i$th dipole. The electric field is defined by
\begin{equation}
\textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) - \frac{k^2}{r_{ij}}\left(\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right)\right\}\frac{e^{ikr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
\label{electric_field_lambda}
\end{equation}
where $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}=|{\bf r}_i-{\bf r}_j|$ and $k=\sqrt{\varepsilon_b}\omega/c.$ The field is decomposed into three parts---the near- ($r_{ij}^{-3}$), intermediate- ($r_{ij}^{-2}$), and far-field ($r_{ij}^{-1}$)---which together include all dipolar retardation effects \cite{Purcell1973}. Interestingly, the latter term carries the opposite sign of the former two. As will be shown in the following, it is because of both the relative magnitude and sign of these terms as well as the oscillatory behavior of $e^{ikr_{ij}}$ that the interactions can change character and switch from energy-lowering to energy-raising.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{fig2.pdf}
\caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer. At small scales $r_0 < 5$ nm the magnetic modes are ordered as predicted using a quasistatic model, with NS (orange) lower in energy than aN (blue). This implies that for very small oligomer systems, the quasistatic approximation is still accurate. However, at sizes greater than $r_0 = 5$ nm and smaller than $r_0 = 20$ nm, the eigenmodes switch order. This is due to the dominance of the far-field term, which is evident from (b and d). Finally, at sizes greater than $r_0 = 20$ nm, the eigenmodes switch order again. Also plotted are simulated peak positions of each mode (dashed lines) to show agreement within 0.1 eV.}
\label{scaling}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{scaling} shows the predicted magnetic plasmon resonance energies from both Eq. (\ref{equation_of_motion}) and full-wave numerical electrodynamics simulation of the 2-mer and 3-mer with increasing $a$ \cite{Hohenester2012}. At small $a$, the magnetic modes preserve the quasistatic ordering predicted in previous work \cite{Cherqui2014}, which is to be expected when the oligomer system fits within an optical wavelength and the near-field dominates the electric field. As the system size increases, the resonance energies decrease and cross at $a \approx 7$ nm, and once more at $a \approx 20$ nm. The second crossing recovers the same spectral ordering as at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is correct again. Rather, both crossings are due entirely to retardation effects as can be seen from the total interaction energy 
\begin{equation}
U = -\frac{1}{2} \sum_{ij} \textbf{d}_i \cdot \textbf{E}_j(\textbf{r}_i),
\label{interactionenergy}
\end{equation}
between each pair of electric dipole plasmons within each magnetic plasmon mode. It is the inclusion of the far-field that causes the mode switching, as it carries the opposite sign of the near- and intermediate-field terms. Fig. \ref{scaling} shows the competition between these field components as well as their relative contributions to the total interaction energy. Inspection of Fig. \ref{scaling}c reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field. Perhaps more interestingly, in any dielectric medium with $\varepsilon_b > 1$ the crossing points are shifted towards smaller scale due to wavelength contraction. This can be explained through the impact of dielectric medium upon the interaction energy $U,$ which increases with increasing $\varepsilon_b$ due mostly to the far-field term's dependence upon $k^2$ \cite{Elsayed2008}. While previous work has explored the oscillatory nature of hybridized electric dipole plasmon resonances and radiation damping as a function of separation in noble metal dimers \cite{vonPlessen2007}, our work shows that magnetic plasmon resonances also oscillate with interparticle separation and can be understood by analysis of the different contributions to the dipole-dipole interaction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{fig3.pdf}
\caption{Magnetic field distributions of a magnetic dipole mode (a) and an electric dipole mode (c) in the xy-plane with corresponding radiation patterns (b and d) in the yz-plane. The magnetic dipole exhibits the expected dipolar doughnut, or two lobe, shape with a node along the z-axis. The electric dipole moment also shows the expected pattern with a node along the y-axis.}
\label{scattering}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{scattering} displays the differential scattering power profiles associated with the aN (a) and NS (b) magnetic plasmon resonances as well as their interference (c) for any $N$-mer with electric and magnetic dipoles oriented as descibed above. Since the aN mode has only a $z$-oriented magnetic dipole, its radiation pattern is orthogonal to that of the $y$-directed electric dipole of the NS mode. This means that asymmetry in the radiation pattern is due to the excitation of both modes. Thus, examination of the radiation directionality allows one to determine the net electric or magnetic dipole character. Such forward/backward scattering asymmetries have been predicted and demonstrated in metal-semiconductor core-shell nanoparticle assemblies, that similarly exploit the interference between electric and magnetic plasmons to direct light \cite{Kivshar2012}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{fig4.pdf}
\caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d). By choosing the beam positions marked on the diagrams and choosing different angles at which to measure the light emitted, the magnetic modes of each oligomer can be disentangled. The colored "x's" correspond to colored traces. The blue traces show a collection angle of $\phi = 3\pi/2$ and the orange traces are for $\phi = \pi$, while both have $\theta = \pi/4$. Simulating these CL experiments with $r_0 = 15$ nm shows the aN modes lower in energy than the NS modes, as predicted. WIth $r_0 = 30$ nm, the modes switch, again as predicted.}
\label{CL_2mer_3mer}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The previous section built up intuition on the directionality of light scattered by the magnetic modes of the 2-mer and 3-mer. This intuition informs the particular angles at which to collect CL spectra. Fig. \ref{CL_2mer_3mer} shows simulated point angle-resolved CL spectra of the 2-mer and 3-mer, with the electron beam position chosen so as to excite the aN (blue) and NS (orange) modes. Note however, due to the symmetry of the oligomers, the blue electron beam position excites not only the aN mode, but also weakly the NS mode. Since the radiation profile of the aN mode is orthogonal to that of the NS mode, it is possible to distinguish them by analyzing the angular distribution of emitted CL radiation. The angle-resolved CL spectra at two such angles are reported in Fig. \ref{CL_2mer_3mer}. These simulated spectra confirm the predictions of the model displayed in Fig. \ref{scaling}; specifically, between $a = 15 - 30$ nm, the aN and NS modes switch spectral order. The simulation also shows mode switching at $a\approx7$ nm, however, the splitting energies are too small to be experimentally detectable with conventional CL. Nevertheless, experimental confirmation of the secondary mode splitting is possible, and would verify both our analytical and numerical predictions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{fig5.pdf}
\caption{Signed magnetic field magnitudes of the modes of the 13-particle (a, b, and c), 19-particle (d, e, and f), and 31-particle (g, h, and i) clusters. Similarly to the 2mer and 3mer from before, we present only those magnetic modes with either NS and electric dipole character (a, b, d, e, g, and h) or with aN and magnetic dipole character (c, f, and i).}
\label{kagan_fields}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{kagan_fields} displays the signed magnetic field magnitude of the aN (panel a) and NS (panel c) magnetic plasmon resonances of the 13-, 19-, and 31-particle nanoclusters. The black arrows denote the electric dipole moments of the individual MNPs within each magnetic plasmon mode, the magenta arrows denote the net electric dipole moment of the nanocluster, and the background color denotes the strength of the associated magnetic field. The net electric or magnetic dipole magnitude is denoted below each panel. Panels b and d display the energy-filtered electron energy-loss (EEL) profiles of these modes. It is important to note that each aN mode is weakly excitable from the middle MNP (as indicated by the low EEL probability surrounding it), while the NS mode is strongly excitable from the same location (as indicated by the high EEL probability surrounding it). In all cases, the NS mode is doubly degenerate as would be true of any structure with sixfold symmetry. In analogy to the oligomers, these magnetic modes are chosen because they are the simplest (i.e., lowest order) and their radiation patterns are spatially orthogonal.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics{fig6.pdf}
\caption{Eigenenergies and interaction energies for the magnetic modes of the 13- (a and b), 19- (c and d), and 31-particle (e and f) clusters. Unlike the 2mer and 3mer, at very small values of $r_0$, the aN modes are lower in energy than the NS modes. However, for each system a crossing point does occur between $r_0 = 30$ nm and $r_0 = 40$ nm. While the modes of the 13-particle system behave as expected, the aN and NS modes of the larger clusters behave contrary to the intuition built from the earlier model systems. At larger sizes, instead of a monotonic decrease in eigenenergies, the modes exhibit an increase in energy. Looking at the interaction energies, it becomes clear that this is again due to retardation effects, as the term that contributes the most anti-bonding character to the total interaction energy is the far-field. Furthermore, the 31-particle system exhibits a second crossing, unlike the other two structures, and the increase in its eigenenergies is maximized at smaller sizes.}
\label{kagan_eigen}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fig. \ref{kagan_eigen} displays the evolution of the aN and NS magnetic resonances with size $a$ as dictated by the model. Here the size-dependent behavior of the nanocluster resonances is different due to the hexagonal packing as opposed to the open-ring structure of the $N$-mer. Nevertheless, the analytic model is capable of predicting the magnetic spectrum. Most surprising is the oscillatory behavior of the nanoclusters' magnetic resonances with size as opposed to the expected monotonic redshifting of those of the $N$-mer (see Fig. \ref{scaling}). Panels b and c display the total interaction energy $U$, and its near-, intermediate-, and far-field contributions, showing that this oscillatory behavior is due to retardation effects through the $e^{ikr_{ij}}$ factor in Eq. (\ref{electric_field_lambda}).
